\noindent I would like to thank my adviser, Professor Honma Kentaro, for bringing me into his laboratory and trusting me to find my way through advanced technologies, technical Japanese language, and the world of academic writing, all of which were unfamiliar to me when I began.

\noindent I am very grateful for receiving the SEUT Grant for International Students. This scholarship enabled me to build a life as a student and as a resident in a vibrant area of Tokyo. My desire to immerse myself in Japanese language and culture  led me to take on  part-time employment as a babysitter. Engaging with the families I have met through this job have enriched my life immensely. Working as a babysitter also resulted in numerous visits to local parks and playgrounds, which broadened my perspective on city life and informed my research more than I could have imagined. 

\noindent Many wonderful people have played a central role in my own social interactions in Tokyo and beyond. Much credit is due to my parents, who fueled my dreams by moving me around the US and the world as a child, giving me the strength to follow those dreams and the courage to make big moves. Thank you to my extended family (including Grandma, Ben, Isa, Jacob, Julia, Hunter, Kathleen, Mark, Ali) and friends (Marisa, Valeria, Brianna, Michele, Alex, George, Jill, Tyler, Olivia, Patrick, Pat, Jessica, Antoinette, Amanda, Danny, and many more) for keeping our relationships close during my time in Tokyo through Facetime calls and messaging. Thanks also to Kritika and Santiago, for sharing my enthusiasm for studying in Tokyo---and for writing their theses first! Finally, thank you to John, my husband, for following me to Japan to live out this adventure together and for accompanying me to "see the activity" of Yoyogi Park, Shinjuku Gyoen, and the countless other public spaces we have discovered across Japan.